---
title: "Data management group assignment"
author: "Beatrice Gervais-Bergeron, Julien Beaulieu, Amelia Hesketh, Masumi Stadler"
date: "24/11/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/media/shared/Documents/University/PhD/Courses/DataManagement/Activity_Session5")
```

# Selected question

Option 1: "Ensure that all higher-level taxonomic information is complete for all invertebrate morphospecies (morphospecies = bwg_names). Note, morphospecies are identified at the lowest level by the researcher (often genus or family). [suggested package: taxize]"

---

# Work flow
## Set-up

First, correctly identify working directory and properly set the directory.
```{r}
# Checking working directory and properly set the correct path
getwd()
```

Next, load needed packages.
```{r}
pkgs <- c("tidyverse", "taxize", "myTAI")
#lapply(pkgs, install.packages, character.only = TRUE)
invisible(lapply(pkgs, library, character.only = TRUE))
rm(pkgs)
```

## Read in data

Read in data and explore if column classes are correct.
```{r, echo=FALSE}
#abundance <- read_csv("./BWG_database/bwgv1_abundance.csv")
traits <- read_csv("./raw_data/bwgv1_traits.csv")

str(traits)
```

## Extract variables of interest and rename to match *taxize*

```{r}
# Number 1:Ensure that all higher level taxonomic information is complete for all 
# invertebrate morphospecies (morphospecies = bwg_names). Note, 
# morphospecies are identified at the lowest level by the researcher (often genus 
# or family). [suggested package: taxize]

# get only taxonomic-related columns with an id key of taxon_name (lowest resolution taxon)
traits_tax <- traits %>% 
  dplyr::select(domain:subspecies, taxon_level,taxon_name) %>% 
  # rename columns so tax_name function can recognize levels
  rename(order = ord, suborder = subord) %>% 
  # only need to run the function on unique combinations of taxa
  distinct()

```

## Retrieve taxonomy information
```{r}
replace_missing_taxa <- function(df){
  clean_data <- data.frame()
  levels_replaced <- c()
  for (row in 1:nrow(df)){
    x <- df[row,]
    col_names <- colnames(x)
    levels_replaced_row <- c()
    #names of columns where taxonomic data are missing
    missing <- data.frame(numbers = which(is.na(x)), names = col_names[which(is.na(x))])
    # find taxonomic information based on lowest taxonomic level identified
    tax_names <- tax_name(x$taxon_name, get = missing$names, db = "ncbi")
    tax_col_names <- colnames(tax_names)
    for (missing_col in 1:nrow(missing)){
      # for every column where a value was missing...
      for (filled_col in 1:length(tax_col_names)){
        # check the completed taxonomic information from the tax_name function
        if (missing$names[missing_col] == tax_col_names[filled_col]){
          # and then fill in the missing data with the completed information if it exists
          if (is.na(tax_names[1, filled_col]) == 0){
            col_ref <- missing$numbers[missing_col]
            x[1, col_ref] <- tax_names[1,filled_col]
            levels_replaced_row <- paste(levels_replaced_row, missing$names[missing_col])
          }
        }
      }
    }
    # assemble all the clean data in a single dataframe
    clean_data <- clean_data %>% 
      rbind(x)
    levels_replaced[row] <- paste(levels_replaced_row, collapse = "")
  }
  # and amalgamate all of the data with the column indicating what has been replaced
  clean_data <- clean_data %>% 
    cbind(levels_replaced)
}
levels_replaced_row <- c()
```

---


## Clean output

```{r}
# now run the function on the taxonomic information for traits
clean_traits <- replace_missing_taxa(traits_tax)

clean_traits_df <- unique(as.data.frame(clean_traits))

write_csv(clean_traits_df, "./clean_data/replaced_taxa.csv")

# some taxa have multiple UID choices, so select the following as the tax_name function runs:
# 2 for Culicoides, 2 for Forcipomyia, 2 for Chironomus, 2 for Polypedilum,
# 1 for Polyphaga, 2 for Culex, 2 for Haemogogus, 2 for Aedes, 1 for Trentepohlia,
# 2 for Tipula, 1 for Ormosia, 2 for Limonia, 2 for Oligochaeta, 2 for Forcipomyia

```


## Combine back with original morphospecies ID
```{r}
traits_complete <- traits %>% 
  # take out incomplete taxonomic data
  select(-(4:17)) %>% 
  # and join with the completed taxonomic data
  full_join(clean_traits) %>% 
  # the tax_name function seems to replace suborder with infraorder sometimes, 
  # so retain only the first instance of replacement for each unique taxon
  distinct(bwg_name, .keep_all = TRUE)

```

## Export csv
```{r}

# taxonomic data are now fully integrated into dataframe

write_csv(traits_complete,"./clean_data/traits_complete.csv")
```

