---
title: "Data management group assignment"
author: "Beatrice Gervais-Bergeron, Juliean Beaulieu, Amelia Hesketh, Masumi Stadler"
date: "24/11/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/media/shared/Documents/University/PhD/Courses/DataManagement/Activity_Session5")
```

# Selected question

Option 1: "Ensure that all higher-level taxonomic information is complete for all invertebrate morphospecies (morphospecies = bwg_names). Note, morphospecies are identified at the lowest level by the researcher (often genus or family). [suggested package: taxize]"

---

# Work flow
## Set-up

First, correctly identify working directory and properly set the directory.
```{r}
# Checking working directory and properly set the correct path
getwd()
```

Next, load needed packages.
```{r}
pkgs <- c("taxize","stringdist", 
          "tidyverse")
#lapply(pkgs, install.packages, character.only = TRUE)
invisible(lapply(pkgs, library, character.only = TRUE))
rm(pkgs)
```

## Read in data

Read in data and explore if column classes are correct.
```{r, echo=FALSE}
#abundance <- read_csv("./BWG_database/bwgv1_abundance.csv")
traits <- read_csv("./raw_data/bwgv1_traits.csv")

str(traits)
```

## Extract variables of interest and rename to match *taxize*

```{r}
# get only taxonomic-related columns with an id key of taxon_name (lowest resolution taxon)
traits_tax <- traits %>% 
  dplyr::select(4:17, 23,24) %>% 
  # rename columns so tax_name function can recognize levels
  rename(order = ord, suborder = subord) 

```

```{r}
# check phylogenetic level names, do they match taxize spelling?
# extract taxize level names
taxize.levs <- rank_ref %>% separate(ranks, into = c("rank","divisions"), sep = ",") %>% 
  select(rank) %>% as_vector()
names(taxize.levs) <- NULL # erase rank numbers saved as vector names

# Extract column names that include phylogenetic level in our database
tax.list <- colnames(taxtab)[2:15]

# apply stringdist function to retrieve best matches to taxize names
i <- adist(tax.list, taxize.levs) %>% 
  apply(1, which.min)

data.frame(tax_original = tax.list,
           tax_repaired = taxize.levs[i]) # looks good

# overwrite
colnames(taxtab)[2:15] <- taxize.levs[i]

# same for taxon_level column
# Extract taxon_level as vector, drop NAs = "Unknown"
tax.list <- taxtab %>% drop_na(taxon_level) %>% select(taxon_level) %>% as_vector()

i <- adist(tax.list, taxize.levs) %>% 
  apply(1, which.min)

data.frame(tax_original = tax.list,
           tax_repaired = taxize.levs[i]) # looks good

# overwrite
taxtab[!is.na(taxtab$taxon_level),"taxon_level"] <- taxize.levs[i]

```

---


## Retrieve taxonomy information


```{r}
# All the taxonomic levels we are looking for
tax.list <- colnames(traits_tax)[1:14]

# get all unique taxon_name
sp.list <-unique(traits_tax$taxon_name)
# get a dataframe with the unique taxon-name and their associated taxa_level 
# to easily answer to the query of taxa_name function
sp.list.tax <- unique(traits_tax[,15:16])

# Create a dataframe with the information on each unique species with the taxa-name function
taxquery <- tax_name(query = c(sp.list), get = tax.list, db = "ncbi")
# when selection offer you the choice between genus and subgenus, 
# select always Genus (#2) for correct classification, since there is no subgenus collected 

# save this object in a csv file to avoid to process it each time (It is time consuming)
write_csv(taxquery,"./clean_data/tax_class.csv")
```

## Clean output

## Combine back with original morphospecies ID

## Export csv
