---
title: "Data management group assignment"
author: "Beatrice Gervais-Bergeron, Juliean Beaulieu, Amelia Hesketh, Masumi Stadler"
date: "24/11/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/media/shared/Documents/University/PhD/Courses/DataManagement/Activity_Session5")
```

# Selected question

Option 1: "Ensure that all higher-level taxonomic information is complete for all invertebrate morphospecies (morphospecies = bwg_names). Note, morphospecies are identified at the lowest level by the researcher (often genus or family). [suggested package: taxize]"

---

# Work flow
## Set-up

First, correctly identify working directory and properly set the directory.
```{r}
# Checking working directory and properly set the correct path
getwd()
```

Next, load needed packages.
```{r}
pkgs <- c("taxize","stringdist", 
          "tidyverse")
#lapply(pkgs, install.packages, character.only = TRUE)
invisible(lapply(pkgs, library, character.only = TRUE))
rm(pkgs)
```

## Read in data

Read in data and explore if column classes are correct.
```{r, echo=FALSE}
#abundance <- read_csv("./BWG_database/bwgv1_abundance.csv")
traits <- read_csv("./BWG_database/bwgv1_traits.csv")

str(traits)
```

## Extract variables of interest and rename to match *taxize*

```{r}
# select only variables of interest
colnames(traits)
(taxtab <- traits %>% select(bwg_name:subspecies, taxon_level))
```

```{r}
# check phylogenetic level names, do they match taxize spelling?
# extract taxize level names
taxize.levs <- rank_ref %>% separate(ranks, into = c("rank","divisions"), sep = ",") %>% 
  select(rank) %>% as_vector()
names(taxize.levs) <- NULL # erase rank numbers saved as vector names

# Extract column names that include phylogenetic level
tax.list <- colnames(taxtab)[2:15]

# apply stringdist function to retrieve best matches to taxize names
i <- adist(tax.list, taxize.levs) %>% 
  apply(1, which.min)

data.frame(tax_original = tax.list,
           tax_repaired = taxize.levs[i]) # looks good

# overwrite
colnames(taxtab)[2:15] <- taxize.levs[i]

# same for taxon_level column
# Extract taxon_level as vector, drop NAs = "Unknown"
tax.list <- taxtab %>% drop_na(taxon_level) %>% select(taxon_level) %>% as_vector()

i <- adist(tax.list, taxize.levs) %>% 
  apply(1, which.min)

data.frame(tax_original = tax.list,
           tax_repaired = taxize.levs[i]) # looks good

# overwrite
taxtab[!is.na(taxtab$taxon_level),"taxon_level"] <- taxize.levs[i]

```

---

##

```{r}
# separate identifier
abundance <- read_csv("./BWG_database/bwgv1_abundance.csv") %>%
  separate(bwg_name, into = c("identified.tax", "number"), sep = "[.]")

levels(factor(abundance$identified.tax))
```

```{r}
# Correct typo
```


## Retrieve taxonomy information


```{r}
# make species names as list
specieslist <- levels(factor(abundance$identified.tax))

# "Oligochaeta" appears both as genus and subclass, select 2 for correct classification
(taxtab <- tax_name(query = c(specieslist), get = c("kingdom","phylum",
                                         "class","order",
                                         "family", "genus"), db = "ncbi"))
```

## Clean output

## Combine back with original morphospecies ID

## Export csv
